Issues in developing mulitvariable models for treatment selection

### 2016-02-23 Documents/paper.Rmd
new method working for sig devel

```{r funcs}
print("Insert simulation results")
```

@@

>>>>

@@

```{r cvsims}
load("../Code/cvsim-result.RData")
cvres <- do.call("rbind", cvsims)
library(tidyr)

cvlong <- do.call("rbind", lapply(1:ncol(cvres), function(i){

  cl <- cvres[, i]
  splow <- strsplit(colnames(cvres)[i], ".", fixed = TRUE)
  nm <- paste(unlist(sapply(splow, function(s) rev(rev(s)[-1]))), collapse = ".")
  cls <- sapply(splow, function(s) rev(s)[1])
  data.frame(value = cvres[, i], stat = cls, scen = nm, stringsAsFactors = FALSE)

}))

ggplot(subset(cvlong, stat == "AUC"), aes(y = value, x = scen)) + geom_violin(fill = "grey60") + 
  theme_bw(base_size = 13, base_family = "serif") + 
  scale_x_discrete("Estimation Approach", labels = c("Bootstrap", "Leave 10 out CV", "Leave 100 out CV", 
                                                     "30% Holdout", "50% Holdout", "Resubstitution", "Partial CV", "Partial Holdout")) + 
  ylab("Area Under the ROC Curve")
```
